Paper_analyses

### 2021-11-25 Paper_Analyses_subj_obje_arousal.Rmd
MFA2.1

namesrepl<- c("ssid", "p_neg", "p_mid" ,"p_pos", "HR_neg" , "HR_mid",
                  "HR_pos","SCR_neg", "SCR_mid", "SCR_pos")

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

namesrepl<- c("ssid", "p_neg", "p_mid" ,"p_pos", "HR_neg" , "HR_mid",
                  "HR_pos","SCR_neg", "SCR_mid", "SCR_pos", "ar_neg","ar_mid", "ar_pos",
              "vl_neg","vl_mid", "vl_pos")

@@

clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$pcscoremaybe <- res.mfa_agg_byval[["global.pca"]][["ind"]][["cos2"]][,1]

clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar<- (clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar_neg+clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar_mid+
  clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar_pos)/3

# cor.test(res.mfa_agg_byval[["global.pca"]][["ind"]][["cos2"]][,3],
#          clustering_new_pre_PCA_2_agg_by_val_sel_dcast2$ar)

@@

colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
res.mfa_agg_byval2 <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
               group = c(1, 3, 3, 3,3,3), 
               type = c("n", "s", "s", "s","s", "s"),
               name.group = c("ssid","pupil","HR","SCR", "AR", "VL"),
               num.group.sup = c(1),
               graph = TRUE)

print(res.mfa_agg_byval2)

```{r}
library("factoextra")
eif_vyval2 <- get_eigenvalue(res.mfa_agg_byval2)
head(eif_vyval2)

the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
```{r}
fviz_screeplot(res.mfa_agg_byval2)

@@

group_vybal2 <- get_mfa_var(res.mfa_agg_byval2, "group")
group_vybal2

The different components can be accessed as follow:
```{r}
# Coordinates of groups
head(group_vybal2$coord)
# Cos2: quality of representation on the factore map
head(group_vybal2$cos2)
# Contributions to the  dimensions
head(group_vybal2$contrib)

@@

```{r}
fviz_mfa_var(res.mfa_agg_byval2, "group")

@@

To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
```{r}
# Contribution to the first dimension
fviz_contrib(res.mfa_agg_byval2, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa_agg_byval2, "group", axes = 2)

```
Quantitative variables
The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables. This function returns a list containing the coordinates, the cos2 and the contribution of variables:
```{r}
quanti.var_agg_by_val2 <- get_mfa_var(res.mfa_agg_byval2, "quanti.var")
quanti.var_agg_by_val2

```{r}
# Coordinates
head(quanti.var_agg_by_val2$coord)
# Cos2: quality on the factore map
head(quanti.var_agg_by_val2$cos2)
# Contributions to the dimensions
head(quanti.var_agg_by_val2$contrib)

@@

```{r}
fviz_mfa_var(res.mfa_agg_byval2, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

@@

```{r}
fviz_mfa_var(res.mfa_agg_byval2, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”). We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
```{r}
fviz_mfa_var(res.mfa_agg_byval2, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"), legend = "bottom")

```{r}
fviz_contrib(res.mfa_agg_byval2, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")
fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 2, top = 20,
             palette = "jco")

@@

ind_agg_byval2 <- get_mfa_ind(res.mfa_agg_byval2)
ind_agg_byval2

@@

```{r}
fviz_mfa_ind(res.mfa_agg_byval2, col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)

fviz_mfa_ind(res.mfa_agg_byval2, 
             habillage = "ssid", # color by groups
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

@@

fviz_mfa_ind(res.mfa_agg_byval2, 
             # habillage = "stimIAPS2", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

@@

```{r}
fviz_mfa_ind(res.mfa_agg_byval2, partial = "all") 
# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:

@@

```{r}
fviz_mfa_axes(res.mfa_agg_byval2)
